TensorAlloy: an automatic atomistic neural network program for alloys

### 2019-08-22 doc/papers/nn/manuscript.tex
Minor update.

\begin{abstract}
Atomistic modeling is important for studying physical and chemical properties of
materials. Recently, machine learning interaction potentials have gained much 
more attentions as they can provide density functional theory level predictions 
within negligible time. The symmetry function descriptor based 
atomistic neural network is the most widely used model for modeling alloys. 
To precisely describe complex potential energy surfaces, integrating advanced 
metrics, such as force or virial stress, into training can be of great help.  
In this work, we propose a virtual-atom approach to model the total energy of 
symmetry function descriptors based atomistic neural network. Our approach 
creates the computation graph directly from atomic positions. Thus, the 
derivations of forces and virial can be handled by TensorFlow automatically and 
efficiently. This new approach is implemented in our program TensorAlloy, which 
supports constructing machine learning interaction potentials for both 
\textit{molecules} and \textit{solids}. The QM7 and SNAP/Ni-Mo datasets are used 
to demostrate the performances of our program.
\end{abstract}

@@

{\bf PROGRAM SUMMARY} \\
\begin{small}
\noindent
{\em Program Title: TensorAlloy} \\
{\em Licensing provisions(please choose one): Apache-2.0}     \\
{\em Programming language: Python 3.7}                        \\
{\em Supplementary material:}                                 \\
{\em Journal reference of previous version:}                  \\
{\em Does the new version supersede the previous version?:}   \\
{\em Reasons for the new version:} \\
{\em Summary of revisions:}*\\
{\em Nature of problem:} \\
  Modeling interatomic interactions with the symmetry function descriptor based
  atomistic neural networks.
{\em Solution method:} \\
  The TensorAlloy program is built upon TensorFlow and the virtual-atom 
  approach. TensorAlloy can build direct computation graph from atomic positions 
  to total energy. Atomic forces and virial stress tensors are handled by 
  TensorFlow automatically and efficiently.
{\em Additional comments including Restrictions and Unusual features}\\
  This program needs TensorFlow 1.13.*. Neither newer or older TensorFlow is 
  supported. \\
\end{small}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table. 3
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table}[h]
\centering
\begin{tabular}{cccc}
\hline
Subset & Energy (meV/atom) & Force (eV/\AA) & Stress (GPa) \\
\hline
Mo & 16.5 (16.2) & 0.28 (0.29) & 0.75 \\
Ni & 4.5 (7.9)   & 0.07 (0.11) & 0.83 \\
Ni$_4$Mo & 4.1 (4.0) & 0.09 (0.14) & 0.98 \\ 
Ni$_3$Mo & 4.5 (5.2) & 0.11 (0.16) & 1.19 \\
Ni$_{\mathrm{Mo}}$ & 12.9 (22.7) & 0.09 (0.13)& 0.34 \\
Mo$_{\mathrm{Ni}}$ & 12.9 (33.9) & 0.12 (0.55)& 0.45 \\
Overall & 10.8 (22.5)& 0.11 (0.23) & 0.59 \\
\hline
\end{tabular}
\caption{\label{table:MAE}
Comparion of the MAEs in predicted energies (mev/atom), forces (eV/\AA) and 
stress (GPa) relative to DFT of each subset for the binary Mo-Ni model and the
corresponding SNAP benchmarks (bracket)}
\end{table}

@@

This work was supported by the National Key Research and Development Program of 
China under Grant No. 2016YFB0201203, the Science Challenge Project under Grant 
No. TZ2018002 and the National Natural Science Foundation of China under Grant 
No. U1630250.

>>>>

\begin{abstract}
Atomistic modeling is important for studying physical and chemical properties of
materials. Recently, machine learning interaction potentials have gained much 
more attentions as they can provide density functional theory level predictions 
within negligible time. The symmetry function descriptor based 
atomistic neural network is the most widely used model for modeling alloys. 
To precisely describe complex potential energy surfaces, integrating advanced 
metrics, such as force or virial stress, into training can be of great help.  
In this work, we propose a virtual-atom approach to model the total energy of 
symmetry function descriptors based atomistic neural network. Our approach 
creates the computation graph directly from atomic positions. Thus, the 
derivations of forces and virial can be handled by TensorFlow automatically and 
efficiently. This new approach is implemented in our open-source program 
TensorAlloy, which supports constructing machine learning interaction potentials 
for both \textit{molecules} and \textit{solids}. The QM7 and SNAP/Ni-Mo datasets 
are used to demostrate the performances of our program.
\end{abstract}

@@

{\bf PROGRAM SUMMARY} \\
\begin{small}
\noindent
{\em Program Title: TensorAlloy} \\
{\em Licensing provisions(please choose one): LGPL}           \\
{\em Programming language: Python 3.7}                        \\
{\em Supplementary material:}                                 \\
{\em Journal reference of previous version:}                  \\
{\em Does the new version supersede the previous version?:}   \\
{\em Reasons for the new version:} \\
{\em Summary of revisions:}*\\
{\em Nature of problem:} \\
  Modeling interatomic interactions with the symmetry function descriptor based
  atomistic neural networks.
{\em Solution method:} \\
  The TensorAlloy program is built upon TensorFlow and the virtual-atom 
  approach. TensorAlloy can build direct computation graph from atomic positions 
  to total energy. Atomic forces and virial stress tensors are handled by 
  TensorFlow automatically and efficiently. \\
{\em Additional comments including Restrictions and Unusual features}\\
  This program needs TensorFlow 1.13.*. Neither newer or older TensorFlow is 
  supported. \\
\end{small}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table. 3
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table}[h]
\centering
\begin{tabular}{cccc}
\hline
\multicolumn{4}{c}{Binary Mo-Ni model} \\
\hline
Subset & Energy (meV/atom) & Force (eV/\AA) & Stress (GPa) \\
\hline
Mo & 16.5 (16.2) & 0.28 (0.29) & 0.75 \\
Ni & 4.5 (7.9)   & 0.07 (0.11) & 0.83 \\
Ni$_4$Mo & 4.1 (4.0) & 0.09 (0.14) & 0.98 \\ 
Ni$_3$Mo & 4.5 (5.2) & 0.11 (0.16) & 1.19 \\
Ni$_{\mathrm{Mo}}$ & 12.9 (22.7) & 0.09 (0.13)& 0.34 \\
Mo$_{\mathrm{Ni}}$ & 12.9 (33.9) & 0.12 (0.55)& 0.45 \\
Overall & 10.8 (22.5)& 0.11 (0.23) & 0.59 \\
\hline
\end{tabular}
\caption{\label{table:MAE}
Comparion of the MAEs in predicted energies (mev/atom), forces (eV/\AA) and 
stress (GPa) relative to DFT of each subset for the binary Mo-Ni model and the
corresponding SNAP benchmarks (bracket)}
\end{table}

@@

This work was supported by the National Key Research and Development Program of 
China under Grant No. 2016YFB0201204, the Science Challenge Project under Grant 
No. TZ2018002 and the National Natural Science Foundation of China under Grant 
No. U1630250.
